\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{28th Nov 2014}

### 2015-02-11 investigation/docs/overview.tex
edits to overview doc

The initial analysis used F-tests and some simulation work to determine the expected Type 1 error rate in the 1st stage of the discovery process. Subsequent simulations and theoretical calculations have suggested that this is not correct when there is a large main effect and / or in the presence of LD. \\

a. Identify which of the two snps in the original epistasis pair has the largest additive effect. Then, treating that as a fixed SNP, perform a genome-wide analysis using the 8df and 4df epistasis model. Use the interaction p-values to determine the empirical distribution of null p-values. This has been completed after filtering all SNPs on the fixed SNPs chromosome as well as +/- 5MB around the position of the original second snp.  \\

b. Identify the largest additive eQTL for the probe (irrespective of effect size). Regress out the effect of the additive loci and use the adjusted phenotype for 8df and 4df model analysis. Results reported are the 8df and 4df of original pair and the empirical p-values from genome-wide analysis fitting each of the two snps as fixed. As before these are determined by filtering out the snps on the same chromosome as the original fixed snp and also within +/- 5MB of the second snp. \\

>>>>

The initial analysis used F-tests and some simulation work to determine the expected Type 1 error rate in the 1st stage of the discovery process. The 1st stage was followed by a 2nd stage where the interaction model was fitted. Subsequent simulations and theoretical calculations have suggested that the Type 1 error rate of the 2nd stage is not correct when there is a large main effect and / or in the presence of LD. \\

a. Identify which of the two snps in the original epistasis pair has the largest additive effect. \\

b. Treat the largest additive SNP as a fixed SNP and perform a genome-wide analysis using the 8df and 4df epistasis model. \\

c. This generates $\approx 500,000$ interaction p-values. Apply the same snp-pair filtering as used in the manuscript. Namely, LD ($r^2$ < 0.1), nclass $=$ 9, and minclass $>$ 5. Any SNP with +/- 5MB of original epistasis SNP pairs were also removed. \\

d.  Use the (filtered) interaction p-values to determine the empirical distribution of null p-values. \\

\newpage

2. Identify the largest additive eQTL for the probe (irrespective of effect size). Regress out the effect of the additive loci and use the adjusted phenotype for 8df and 4df model analysis. Results reported are the 8df and 4df of original pair and the empirical p-values from genome-wide analysis fitting each of the two snps as fixed. As before these are determined by filtering out the snps on the same chromosome as the original fixed snp and also within +/- 5MB of the second snp. \\
